Fig6

### 2020-04-15 analysis/figure-6.Rmd
file for victoria

```{r writefiles}
write.csv(candidatevsd, "../../musicalgenes/data/candidatecounts.csv")
```

>>>>

```{r writefiles}
#write.csv(candidatevsd, "../../musicalgenes/data/candidatecounts.csv")

# for victoria
prlmanip <- candidatevsd %>%
  filter(gene == "PRL", 
         treatment %in% c("extend", "m.inc.d8"))
write.csv(prlmanip, "../results/prlmanip.csv")
```
